---
title: "Homework 7"
author: "Raymond Looney"
date: "2/28/2018"
output: html_document
---

# **Normal Distribution**

##Function to create data
```{r,message=FALSE}
dataCreate <- function(mean1=208.3, mean2=200.4, n1=200, n2=200, sd1=23, sd2=20){
  mydf <- data.frame(control=rnorm(mean = mean1, n=n1, sd=sd1),
                     test=rnorm(mean=mean2, n=n2, sd=sd2))
  return(mydf)
}
myDF <-dataCreate(mean1=100.59)
head(myDF)
```


##Function for ANOVA
```{r,message=FALSE}
library(reshape2)

myDF2 <- melt(myDF) 
ANOVA <- function(data=myDF2){
  myANOVA <- aov(value~variable, data=data)
  summary(myANOVA)
}
ANOVA(data=myDF2)
ANOVA()
myANOVA <- aov(value~variable, data=myDF2)
summary(myANOVA)

```


##Function to create box plot
```{r,message=FALSE}
library(ggplot2)
library(ggplot2)
ANOVAPlot <- function(data=myDF2){
  ggplot(data=data,aes(x=variable, y=value, fill=variable)) + geom_boxplot()
}
ANOVAPlot()

```


## Running ANOVA with the same mean values
```{r,message=FALSE}
df5 <- dataCreate(mean1=375.5, mean2=375.5)
df5<-melt(df5)
ANOVA(data=df5)
ANOVAPlot(df5)
```

### When mean is the same for both variables, and sampling size is the same for both variables, the p-value is always insignificant and over 0.1, but less than 1.0.


## Running ANOVA with different mean values, to get p approximately euqal to 0.05 
```{r,message=FALSE}
df6 <- dataCreate(mean2=204)
df6<-melt(df6)
ANOVA(data=df6)
ANOVAPlot(df6)
```

#### With a difference in mean of approximately 4 ("effect size"), the p-value was found to be below 0.049 9/10 times, making it significant, however, it being a random data set, the p-value changes with each run, sometimes being slightly over, or slightly less than 0.05. 



## Running ANOVA with different sampling size values, to get p approximately equal to 0.05 
```{r,message=FALSE}
df7 <- dataCreate(n2=100)
df7<-melt(df7)
ANOVA(data=df7)
ANOVAPlot(df7)
```

#### When sampling size is lowered by 100 for one variable ("effect size"), the p-value was found to be below or around 0.05, there was much variation, but the data cannot be run anywhere between n2=100-199.




## Running ANOVA with different variance values to get p approximately equal to 0.05
```{r,message=FALSE}
df8 <- dataCreate(sd1=19.1)
df8<-melt(df8)
ANOVA(data=df8)
ANOVAPlot(df8)
```

#### When variance value is changed, the p-value is closest to 0.05 with a change of ~1 ("effect size") from sd1, to sd2. 




#  **Uniform Distrubution** 

```{r,message=FALSE}
dataCreate2 <- function(min1=100.44, min2=120.12, n1=600, n2=600, max1=304.72, max2=315.45){
  mydf <- data.frame(control=runif(min = min1, n=n1, max=max1), test=runif(min=min2, n=n2, max=max2))
  return(mydf)
}
myDFU <-dataCreate2(min1=180.44)
head(myDFU)

```

##New ANOVA Function 
```{r,message=FALSE}
library(reshape2)
myDFU2 <- melt(myDFU) 
ANOVA <- function(data=myDFU2){
  myANOVA <- aov(value~variable, data=data)
  summary(myANOVA)
}

ANOVA(data=myDFU2)
ANOVA()
myANOVA <- aov(value~variable, data=myDFU2)
summary(myANOVA)
```

## Boxplot Function
```{r,message=FALSE}
library(ggplot2)
uniformBOXPLOT <- function(data=myDFU2){
  ggplot(data=data,aes(x=variable, y=value, fill=variable)) + geom_boxplot()
}
uniformBOXPLOT()
```
