---
title: "Homework 6"
author: "Raymond Looney"
date: "2/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read Data
```{r}
z <- read.table("MyDataFile.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)
head(z)
```

##Download ggplot2 and MASS
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

## Create a Histogram
```{r}
p1 <- ggplot(data=z, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

## Add Empirical Density Curve
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

```

## Find Mean and Standard Deviation of rnorm
```{r}
normPars <- fitdistr(z$Height,"normal")
print(normPars)

```

## Find Maximum Likelihood Parameters
```{r}
str(normPars)

normPars$estimate["mean"]
```

## Add Normal Probability Curve
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Height),len=length(z$Height))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Height), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

## Add Exponential Curve
```{r}
expoPars <- fitdistr(z$Height,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$Height), args = list(rate=rateML))
 p1 + stat + stat2
```

## Add Uniform Probability Curve
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$Height), args = list(min=min(z$Height), max=max(z$Height)))
 p1 + stat + stat2 + stat3
```

## Add Gamma Probability Curve
```{r}
gammaPars <- fitdistr(z$Height,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="goldenrod", n = length(z$Height), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

## Add Beta Probability Curve
```{r}
pSpecial <- ggplot(data=z, aes(x=Height/(max(Height + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Height/max(z$Height + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$Height), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

## Comparing log likelihoods: higher is better!
```{r}
normPars$loglik
gammaPars$loglik
expoPars$loglik
```
## Gamma Wins!


##Maximum Likelihood Parameters
```{r}
gammaPars <- fitdistr(z$Height,"gamma")
print(gammaPars)
```

## Create a Simulated Data Set
```{r}
x <- rgamma(n=86,shape=14.07,scale=1/0.124)
x <- data.frame(1:86,x)
names(x) <- list("GroupID","Height")
x <- x[x$Height>0,]
str(x)
```

## Make a Histogram for Simulated Data
```{r}
p1 <- ggplot(data=x, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

## Simulated Gamma Probability Distribution Curve
```{r}
gammaPars <- fitdistr(x$Height,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="goldenrod", n = length(x$Height), args = list(shape=shapeML, rate=rateML))
 p1 + stat4
```

## Recreate Normal Data Gamma Curve
```{r}
z <- read.table("MyDataFile.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)

p1 <- ggplot(data=z, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 


gammaPars <- fitdistr(z$Height,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="goldenrod", n = length(z$Height), args = list(shape=shapeML, rate=rateML))
 p1 + stat4
```

## How Do They Differ?
### I believe that the simulated data graph was very closely related to the actual data graph. The probability curves, and shape of the graphs were extremely similar. The only main difference, was R made the graph "fit" the curve better, and made the graph look more aesthetically pleasing. Overall, the simulated data was a good match for the original, however, I had a small data set, which may have created less room to create a different looking graph.