---
title: "Homework 11"
author: "Raymond Looney"
date: "4/4/2018"
output: html_document
---

# 1. 
```{r}
library(ggplot2)
# N(t)= N(0)e^(r)(t)

################################
# FUNCTION: Exponential Population Growth
# 
# Input: N(0)= Initial population size
#        e= Eulers Number
#        r= Intrinsic rate of increase
#        t= time
# Output: N(t)= Population size at time t
#---------------------------

ExponentialCurve <- function(N0=20,
                             r=0.5,
                             t=1:10) {
Nt <- N0*exp(r*t)
return(Nt)
}
head(ExponentialCurve())  


  
########################################################
# FUNCTION: ExponentialCurvePlot
# plot an Exponential Curve
# Input: N(0)= Initial population size
#        e= Eulers Number
#        r= Intrinsic rate of increase
#        t= time
# Output: graphical representation of exponential growth
#-------------------------------------------------------
ExponentialCurvePlot <- function(N0=20,
                             r=0.5,
                             t=1:10) {
plot(x=t,y=N0*exp(r*t), 
     type="p", #line
     xlab="Time",
     ylab="Nt",
     ylim=c(0,3000))
#mtext(paste("t =",t,"r =",r),cex = 0.7)
return()
}  
ExponentialCurvePlot()  

```


#2.
```{r}
#preliminaries
library(ggplot2)
library(TeachingDemos)
char2seed("April Foolz")

########################################################
# FUNCTION: readData
# read in data frame
# input: file name 
# output: 3-column data frame of observed data (ID, xj, y)
#-------------------------------------------------------
mydF <- read.csv("hw11.csv")
readData <- function(z=NULL) {
             if(is.null(z)) {
               xVar <- mydF$xVar
               yVar <- mydF$yVar
               dF <- data.frame(ID=seq_along(xVar),xVar,yVar) }
  
               return(dF) 
}
readData()              
  
########################################################
# FUNCTION: getMetric
# calculate metric for randomization test
# input: 3-column data frame for regression
# output: regression slope
#-------------------------------------------------------
getMetric <- function(z=NULL) {
              if(is.null(z)) {
                xVar <- mydF$xVar
               yVar <- mydF$yVar
                z <- data.frame(ID=seq_along(xVar),xVar,yVar) }
  
  . <- lm(z[,3]~z[,2])
  . <- summary(.)
  . <- .$coefficients[2,1]
  slope <- .
  return(slope)

}
getMetric()

########################################################
# FUNCTION: shuffleData
# randomize data for regression analysis
# input: 3-column data frame (ID,xVar,yVar)
# output: 3-column data frame (ID,xVar,yVar)
#-------------------------------------------------------
shuffleData <- function(z=NULL) {
                 if(is.null(z)) {
                 xVar <- mydF$xVar
                 yVar <- mydF$yVar
                 z <- data.frame(ID=seq_along(xVar),xVar,yVar) }
z[,3] <- sample(z[,3])
return(z)
}
shuffleData()

########################################################
# FUNCTION: getPVal
# calculate p value for observed, simulated data
# input: -list of observed metric 
#        -vector of simulated metric
# output: lower, upper tail probability vector
#-------------------------------------------------------
getPVal <- function(z=NULL) {
            if(is.null(z)){
              z <- list(xObs=runif(1), xSim=runif(1000)) }
  
  pLower <- mean(z[[2]] <=z[[1]])
  pUpper <- mean(z[[2]] >=z[[1]])
  
  return(c(pL=pLower,pU=pUpper))
  
}
getPVal()
#----------------------------------------------
# main body of code
nSim <- 1000 # number of simulations
Xsim <- rep(NA,nSim) # will hold simulated slopes

dF <- readData()
Xobs <- getMetric(dF)

for (i in seq_len(nSim)) {
  Xsim[i] <- getMetric(shuffleData(dF))}

slopes <- list(Xobs,Xsim)
getPVal(slopes)


########################################################
# FUNCTION: plotRanTest
# ggplot graph
# input: list of the observed metric and vector of simulated metric
# output: ggplot graph
#-------------------------------------------------------
plotRanTest <- function(z=NULL) {
                if(is.null(z)){
                z <- list(xObs=runif(1), xSim=runif(1000)) }
  
dF <- data.frame(ID=seq_along(z[[2]]),
                 simX=z[[2]])
p1 <- ggplot(data=dF,mapping=aes(x=simX))
p1 + geom_histogram(mapping=aes(fill=I("darkorchid"), color=I("black"))) + geom_vline(aes(xintercept=z[[1]],col="blue"))
}
plotRanTest(slopes)
plotRanTest()

```

# 3.
```{r}
ANOVARead<- aov(xVar~yVar, data=readData())

ANOVAShuffle <- aov(xVar~yVar, data=shuffleData())

summary(ANOVARead)
summary(ANOVAShuffle)

```

### Changing the char2seed() at the very beginning changes the p-value of the shuffled data, but not the original data. The function sets a seed for the random number generator from a given character string. Thus a longer char2seed, or a shorter one, or one with different letters will always give different values. However, once this char2seed is expressed, everyone who uses it will get the same "random data".
