---
title: "Leaflet Basics"
author: "Raymond Looney"
date: "4/24/2018"
output: html_document
---


#Leaflet:

### Leaflet is a way to create interactive maps. leaflet() creates a map widget that can store variables in order to modify the map later on


###Installation & Preliminaries
```{r,results="hide"}
#install.packages("leaflet"); comment out in order to knit
library(leaflet)
library(ggplot2)
library(maps)
dF <- read.csv("leafletData30.csv")
dF2<- read.csv("leafletData500.csv")
cities<- read.csv("cities.csv")
library(TeachingDemos)
char2seed("Professor Looney")
```

###How to create a simple map of the earth & piping

```{r}
# addTiles() adds mapping data from Open Street Map
# %>% takes the output my_map,and adds or "pipes" to the next command addTiles() as the first argument, and reassigns it to that variable
my_map <- leaflet() %>%
  addTiles() 

#Without piping notation.
my_map=leaflet()
my_map= addTiles(my_map)

my_map

```


### Different types of maps, and how to incorportate them into your data.
```{r}
#Link:
#http://leaflet-extras.github.io/leaflet-providers/preview/index.html

#Satellite
#my_map %>% addProviderTiles(providers$Esri.WorldImagery)

#Topography Map
#my_map %>% addProviderTiles(providers$OpenTopoMap)

#National Geographic World Map
#my_map %>% addProviderTiles(providers$Esri.NatGeoWorldMap)

### Adding map to my_map
my_map <- leaflet() %>%
  addTiles() %>%
  addProviderTiles(providers$Esri.WorldImagery)
my_map
```

### Adding Markers and Pop-up Text
#### This can be used to label certain areas that samples were collected for an in-field experiment.
```{r}
#Guess who!
map <- my_map %>%
  addMarkers(lat=44.4764, lng=-73.1955)
map

#Give her a label
map <- my_map %>%
  addMarkers(lat=44.4764, lng=-73.1955,
             popup="Bio381 Classroom") # adds a pip up
map

  leaflet()%>%
  addTiles()%>%
  addCircleMarkers(lat=44.4764, lng=-73.1955,
                   popup="Bio381 Classroom")

```

###Adding Many Markers
####Adding 1 marker at a time isn't practical all the time. Create a random data file, or insert a .csv file with 2 variables: latitude (lat) and longitude (lng)
```{r}
# Let's say I wanted to collect  data randomly in Centennial Woods.
                            # Create a random data frame:
df <- data.frame(lat= runif(20, min=44.4770, max=44.4793),
                 lng= runif(20, min=-73.18788, max=-73.18203))
head(df) 
df %>%
  leaflet() %>% #passes argument to make map
  addTiles() %>% # Adds mapping data from Open Street Map
  addMarkers() #Adds markers

                             #Importing a .csv file
# dF is a data frame with 30 coordinates in it
markers <- data.frame(lat= dF$lat,
                 lng= dF$lng)
head(markers) 

markers %>%
  leaflet() %>% #passes argument to make map
  addTiles() %>% # Adds mapping data from Open Street Map
  addMarkers() #Adds markers

```

###Adding Circle Markers 
```{r}
markers%>%
  leaflet()%>%
  addTiles()%>%
  addCircleMarkers()
```

### Adding Legends:
#### A. rubrum= Red Maple
#### T. canadensis= Eastern Hemlock
#### P. strobus= White Pine
```{r}
# add what colors you want. If this doesnt appear you get shadows on the map.
df <- data.frame( col = sample(c("red", "blue", "green"),
                               20, replace = TRUE),
                 stringsAsFactors = FALSE)

markers %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = c("A. rubrum", "T. canadensis", "P. strobus"), colors = c("blue", "red", "green")) 
#assign color to tree species
```


###Making Clusters
```{r}
#dF2 is a data frame with 500 coordinates
cluster <- data.frame(lat= dF2$lat,
                 lng= dF2$lng)
cluster%>%
  leaflet()%>%
  addTiles()%>%
  addMarkers(clusterOptions=markerClusterOptions())
```


###Making Custom Markers
```{r}
# copy and paste!!!
uvmIcon <- makeIcon(iconUrl = "UVM.jpg", # call the image
                    iconWidth = 31*215/230,
                    iconHeight= 31,
  iconAnchorX= 31*215/230/2,
  iconAnchorY= 16
) # what i found to be the best length,height,width for marker
UVMLatLong <- data.frame(
  lat= c(44.4779),
  lng= c(-73.1965)) #lat & lng for your data point 
UVMLatLong %>%
  leaflet()%>%
  addTiles()%>%
  addMarkers(icon= uvmIcon) # what icon do u want

```

### Adding Shapes
```{r}
# you can add rectangles or polygons with addRectangles() or addPolygons()

#POLYGONS
# simple colored map of the united states
mapStates = map("state", fill = TRUE, plot = FALSE)
leaflet(data = mapStates) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)

#CIRCLES
print(cities) # data set with cities, lng, lat, and population.

leaflet(cities) %>% addTiles() %>%
  addCircles(lng = ~long, lat = ~lat, weight = 1,
             radius = ~sqrt(pop) * 30, popup = ~city)
# radius of circle is sqrt of population size, making it span all areas around the midpoint.
```




